---
title: 'Course Project: Shiny Application and Reproducible Pitch'
author: "Vishal Singh"
date: "11/02/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Mtcars Analysis Report

Mtcars Data Analysis Report enabled developing data products using shiny apps being embedded within RMarkDown.

Using PageUp and PageDown keys all the slides can be traversed.


## Application Overview

- Mtcars Properties can be analyzed using several Parameters.
- mpg,Cyl,hp,gear are some of the common parameters.
- This Report enables to pick the right parameters for the best Mtcars selection.


## Slide with Complete Reporting Appliaction

Click the Below Link for the Application.

https://vishal9743.shinyapps.io/Shiny_Application/

Click the link below for compiled project files on github repo.

https://github.com/vishal9743/Shiny-Application-and-Reproducible-Pitch



## Data Used
The data used for this application is mtcars data set. Containing information about 32 cars with 12 variables.

```{r, echo=TRUE}
mtcars$cars <- row.names(mtcars)
row.names(mtcars) <- NULL
head(mtcars)
```

















